The Castro AMR Simulation Code: Current and Future Developments

### 2019-10-02 astronum_2019_Castro/astronum-castro-2019.tex
mor eedits

\section{Example Application}

The SDC approach was demonstrated in \cite{castro:sdc} through a large
suite of convergence tests and a thermonuclear flame problem.

We've run XRB on GPUs and with SDC

>>>>

\section{Example Application: X-ray bursts}

Both the new SDC method and GPU offloading are important to our
science goals, in particular the problem of modeling a flame spreading
across the neutron star during an X-ray burst (XRB).  We discussed the
computational challenges of modeling these events in
\cite{astronum:2018}.  In short: the largest scale we need to model is
the size of the neutron star, or atleast several times the scale at
which rotation and the lateral flame spreading balance (the Rossby
length).  The smallest scale we need to model is dictated by
accurately capturing the burning---we are interested in both the
energy release and nucleosynthesis.  Our first set of two-dimensional simulations
(Eiden et al.\ in preparation) used two physical approximations to
make the problem more tractable.  First, we used a higher rotation
rate than expected in order to reduce the Rossby length, allowing us
to model a smaller region of that star.  Second, we artificially
boosted the speed of the flame to reduce the duration we need to
model.  Our next set of calculations will relax these approximations.

With the new fourth-order accurate reactive hydro solver, we believe
we can capture the dynamics of the spreading flame accurately with one
less refinement level.  This will allow us to expand to larger domains
while keeping the memory demands reasonable.  Figure~XX shows a
simulation of the flame spreading done with the second-order SDC
solver (the 4th order solver does not yet work with axisymmetry),
demonstrating that the SDC framework can evolve this system.

The large increase in performance of the code when run on GPUs enables
us to do away with the flame boosting.  Preliminary estimates show
